\documentclass[a4paper]{article}
\usepackage[pdftex]{graphicx}	% compresses EPS files for PDF's
\usepackage[left=2cm,top=2cm,right=2cm,bottom=3cm,nohead]{geometry}
\usepackage{amsmath}
\usepackage{hyperref}
\begin{document}
\title{Experimental RBC models with portfolio flows}
\author{Haakon Kavli}
\maketitle
\begin{abstract}
Experimental RBC models with portfolio flows. 
\end{abstract}

\section{Document Summary}
Experimental RBC models with portfolio flows. The most recent version is in section 1, the previous version in section 2, and so on. Each section begins with a summary of the goals for that particular section, changes from previous sections, and results. 

\subsection{Notation:} 
\begin{align*}
&c^{ij} = \text{household } i \text{'s consumption of good from country } j \\
&s^{ij} = \text{household } i \text{'s investment in shares from country } j \\
&p^{i} = \text{price on shares in country } i \\
&d^{i} = \text{dividends paid (output) from shares in country } i\\
&r = \text{risk free rate on one period foreign bond}\\
&R = \text{price of foreign one period bond }\equiv \frac{1}{1+r}\\
&b = \text{foreign government bond issuance (= bond holding by foreign households)}\\
&g = \text{government taxes levied on foreign households}\\
&\text{Key parameters:}\\
&\Phi^{i}_s = \text{household } i \text{'s cost of holding (squared) shares in }home\\
&\tau_c = \text{cost of importing (squared) consumption good }
\end{align*}


\section{Simple two country RBC with two assets and quadratic holding cost and import cost}\label{SimplifySquareTax}
\textbf{commit: none}
\subsection{Summary}
\subsubsection{Section Goals}
\begin{itemize}
\item Section goal: Simplify model from section \ref{SquareTax}, below.
\item Change from section \ref{SquareTax}:  In this section I remove one asset (foreign shares) to see if it enables Dynare to solve for equilibrium holdings. 
\item Base model: Two country RBC with exogenous dividends in shares and a global risk free one period bond.
\end{itemize}

\subsubsection{Section Result:}
\begin{itemize}
\item Still no Dynare solution in steady state (could solve manually)
\end{itemize}

\subsection{Foreign household}
The foreign household is the only change to the model from section \ref{SquareTax}. I simply remove the foreigh shares and add exogenous dividends directly in the budget constraint. 

\begin{align*}
&\max \Sigma_{i=0}^\infty \beta^i E_t \bigg(\ln(c^{ff}_{t+i})+ \ln(c^{fh}_{t+i}) \bigg)\\ &\text{s.t}\\
&c^{ff}_t+c^{fh}_t+\frac{\tau_c}{2}(c^{fh}_t)^2+ p^{h}_t s^{fh}_t+\frac{\Phi^f_s}{2}(s^{fh}_t)^2 + R_t b_t=g_t+s^{fh}_{t-1}(p^{h}_t+d^{h}_t)+d^{f}_t+b_{t-1}\\
& \text{where the bond price is a function of the interest rate, $r_t$:}\\
&R_t \equiv \frac{1}{1+r_t}
\end{align*}
Solve:
\begin{align*}
&c^{ff}_t=c^{fh}_t(1+\tau_c c^{fh}_t)\\
&p^{h}_t=\beta E_t \bigg[\frac{c^{ff}_t}{c^{ff}_{t+1}} \bigg(  p^{h}_{t+1}+d^{h}_{t+1} \bigg) \bigg] - \Phi^{f}_s s^{fh}_t\\
&R_t=\beta E_t \bigg[\frac{c^{ff}_t}{c^{ff}_{t+1}} \bigg] 
\end{align*}





























\section{Simple two country RBC with three assets and quadratic holding cost and import cost}\label{SquareTax}
\textbf{commit:25e4abd166a2ce1be4e56b9eb9f54c55848fa75d}
\subsection{Section goals and results}
\subsubsection{Section summary}
\begin{itemize}
\item Section goal: Build upon model from section \ref{HoldingCost}, below. In this section I alter the import tax to ensure a steady state solution for consumption. All other variables had unique steady state solution in section \ref{HoldingCost}.
\item Change from section \ref{HoldingCost}: Quadratic import tax (makes no empirical sense, but get rationale later??). 
\item Base model: Two country RBC with exogenous dividends in shares and a global risk free one period bond.
\end{itemize}

\subsubsection{Section Result:}
\begin{itemize}
\item Successfully solved steady state manually and with fsolve in matlab. 
\item Even by plugging steady state values into Dynare it still won't solve. 
\item Next step: Figure out what is the problem in Dynare?? Or write own program to calculate and plot impulse responses. 
\end{itemize}



where $i,j$ are either $h$ for $home$ or $f$ for $foreign$. The $foreigner$ pays no holding cost on foreign assets, but does pay holding cost on $home$ shares. 


\subsection{Home household}
\emph{Home} household owns domestic shares and spends dividends or sell assets to consume. In aggregate, consumption of \emph{home} goods cannot exceed \emph{home} share dividends. Note that $foreigners$ can consume \emph{home} goods and \emph{home} household can consume \emph{foreign} goods. $Home$'s current account deficit will be funded by selling \emph{home} shares to foreigners, and vice versa. The import tax and holding cost must be paid in the consumption good / asset that is purchased (see aggregate budget constraint in equations \ref{aggregatebc} and \ref{aggregatebcc}).
 
\linebreak
\linebreak



\begin{align*}
&\max \Sigma_{i=0}^\infty \beta^i E_t \bigg(\ln(c^{hh}_{t+i})+ \ln(c^{hf}_{t+i}) \bigg)\\ &\text{s.t}\\
&c^{hh}_t+c^{hf}_t + \frac{\tau_c}{2} (c^{hf}_t)^2 + p^{h}_t s^{hh}_t+\frac{\Phi^h_s}{2}(s^{hh}_t)^2 =s^{hh}_{t-1}(p^{h}_t+d^{h}_t)\\
\end{align*}
Solve:
\begin{align}
&c^{hh}_t=c^{hf}_t(1+\tau_c c^{hf}_t)\\
&p^{h}_t=\beta E_t \bigg[\frac{c^{hh}_t}{c^{hh}_{t+1}} \bigg(  p^{h}_{t+1}+d^{h}_{t+1} \bigg) \bigg] - \Phi^h_s s^{hh}_t
\end{align}




















\subsection{Foreign household}
The \emph{Foreign} household owns $home$ shares, \emph{foreign} shares and \emph{foreign} bonds. They spend dividends or sell assets to consume. In aggregate, consumption of \emph{foreign} goods cannot exceed \emph{foreign} share dividends. There are no holding cost on \emph{foreign} assets. 

\begin{align*}
&\max \Sigma_{i=0}^\infty \beta^i E_t \bigg(\ln(c^{ff}_{t+i})+ \ln(c^{fh}_{t+i}) \bigg)\\ &\text{s.t}\\
&c^{ff}_t+c^{fh}_t+\frac{\tau_c}{2}(c^{fh}_t)^2+ p^{h}_t s^{fh}_t+\frac{\Phi^f_s}{2}(s^{fh}_t)^2 + p^{f}_t s^{ff}_t+ R_t b_t=g_t+s^{fh}_{t-1}(p^{h}_t+d^{h}_t)+s^{ff}_{t-1}(p^{f}_t+d^{f}_t)+b_{t-1}\\
& \text{where the bond price is a function of the interest rate, $r_t$:}\\
&R_t \equiv \frac{1}{1+r_t}
\end{align*}
Solve:
\begin{align}
&c^{ff}_t=c^{fh}_t(1+\tau_c c^{fh}_t)\\
&p^{h}_t=\beta E_t \bigg[\frac{c^{ff}_t}{c^{ff}_{t+1}} \bigg(  p^{h}_{t+1}+d^{h}_{t+1} \bigg) \bigg] - \Phi^{f}_s s^{fh}_t\\
&p^{f}_t=\beta E_t \bigg[\frac{c^{ff}_t}{c^{ff}_{t+1}} \bigg(  p^{f}_{t+1}+d^{f}_{t+1} \bigg) \bigg]\\
&R_t=\beta E_t \bigg[\frac{c^{ff}_t}{c^{ff}_{t+1}} \bigg] 
\end{align}













\subsection{Foreign Government}
\emph{Foreign} government issues risk free one period bond. The bond issuance is autoregressive with long run mean of $\bar b$. The interest payments are paid by lump sum taxes ($g_t$) levied on \emph{foreign} households.
\begin{align}
&b_{t} = \bar b(1-\alpha^b) + \alpha^b b_{t-1} + \epsilon^b_t\\
&g_t	   = R_t b_{t}-b_{t-1}
\end{align}


\subsection{Firms}
Firms are exogenous and pay an autoregressive dividend with long run mean $\bar d^i$. The dividend is the output in the respective country and all consumption of domestic goods plus payment in taxes and adjustment costs, must be paid with this consumption good (see aggregate budget constraints below).
\begin{align}
&s^{fh}_t+s^{hh}_t=1\\
&d^h_t=\bar d^h (1-\alpha^{sh}) +\alpha^{sh}_d d^h_{t-1} + \epsilon^{sh}_{t}\\
&d^f_t=\bar d^f (1-\alpha^{sf}) +\alpha^{sf}_d d^f_{t-1} + \epsilon^{sf}_{t}\\
\end{align}

\subsection{Aggregate budget constraints}
Consumption of \emph{home} goods plus \emph{home} costs and taxes cannot exceed \emph{home} output (dividend). The same holds for \emph{foreign}.
\begin{align}
&c^{hh}_t+c^{fh}_t + \frac{\tau_c}{2} (c^{fh}_t)^2 +\frac{\Phi^{h}_s}{2}(s^{hh})^2 + \frac{\Phi^f_s}{2}(s^{fh})^2 =d^h_t \label{aggregatebc} \\
&c^{hf}_t + c^{ff}_t + \frac{\tau_c}{2} (c^{hf}_t)^2 = d^f_t \label{aggregatebcc}
\end{align}


\subsection{Steady State Solution}
First initialize exogonous variables:
\begin{align*}
\bar s^{ff}&=1\\
\bar b &= 1\\
\bar d^h &= 1\\
\bar d^f &=1
\end{align*}
Then find analytical solutions as function of exogneous variables and parameters:
\begin{align*}
\bar R&=\beta \\
\bar s^{hh} &= \frac{\frac{\phi^{sf}}{\phi^{sh}}}{1+\frac{\phi^{sf}}{\phi^{sh}}}\\
\bar s^{fh} &= 1 -\frac{\frac{\phi^{sf}}{\phi^{sh}}}{1+\frac{\phi^{sf}}{\phi^{sh}}}\\
\bar p^h &= \frac{\beta  \bar d^h -\phi^{sh}*s^{hh}}{1-\beta}\\
\bar p^f &= \frac{\beta \bar d^f}{1-\beta}\\
\bar g&=\bar b(1-\beta)
\end{align*}
Then use \url{fsolve} in Matlab to solve the nonlinear system of equations that determine steady state consumption:

\begin{align*}
0 &= \bar c^hf{} -\bar c^{hh} + \tau_c (\bar c^{hf})^2\\
0 &= \bar c^{fh} -\bar c^{ff} + \tau_c (\bar c^{fh})^2\\
0 &=\bar d^h -\bar c^{hh} - c^{fh} - \frac{\tau_c}{2} (\bar c^{fh})^2 - K\\
0 &=\bar d^f -\bar c^{ff} - c^{hf} - \frac{\tau_c}{2} (\bar c^{hf})^2 - K\\
& \text{where:} \\  
K &\equiv \frac{\Phi^f_s}{2}(\bar s^{fh})^2 + \frac{\Phi^h_s}{2}(\bar s^{hh})^2
\end{align*}
Where the first two equations are the Euler equations, and the last two are the aggregate budget constraints. 

As an example, we can calibrate the parameters to:

\begin{align*}
& \beta = 0.9975
& \phi^{sh} = 1 \\
& \phi^{sf} = 2 
& \tau_c = 0.1\\
\end{align*}
which gives the following steady state values:
\begin{align*}
& \bar R=0.9975
& \bar s^{hh} = 0.6667 \\
& \bar s^{fh}= 0.3333
& \bar p^h = 132.333\\
& \bar p^f = 399
& \bar g = 0.0025 \\
& \bar c^{hh}= 0.336
& \bar c^{hf} = 0.3254\\
& \bar c^{fh} = 0.3254
& \bar c^{ff} = 0.336
\end{align*}
\emph{But for some reason Dynare does not find a steady state even if I initialize all values at the steady state solution!!! Why???}



\newpage






\section{Create downward sloping demand for assets}\label{HoldingCost}
\subsection{Section goals and results}
\subsubsection{Section summary}
\begin{itemize}
\item Overall goal: Build DSGE with unique steady state solution. Model should include \emph{foreign} and domestic sector, and describe portfoli flows. 
\item Section goal: Ensure downward sloping \emph{home} and \emph{foreign} demand for shares and bonds in steady state. 
\item Tool: Quadratic cost of holding bonds and shares. 
\item Base: RBC with exogenous dividends in shares and a global risk free one period bond
\end{itemize}

\subsubsection{Section Result:}
\begin{itemize}
\item Successfully find downward sloping demand for assets
\item Successfully solve steady state for all variables by consumption
\item To solve consumption: Must alter import tax function or utility function
\end{itemize}

\subsection{Home household}
\emph{home} household owns domestic shares and spends dividends or sell assets to consume. In aggregate, consumption of \emph{home} goods cannot exceed \emph{home} share dividends. Note that foreigners can consume \emph{home} goods and \emph{home} household can consume \emph{foreign} goods. The current account deficit will be funded by selling \emph{home} shares to foreigners. 

\begin{align*}
&\max \Sigma_{i=0}^\infty \beta^i E_t \bigg(\ln(c^{hh}_{t+i})+ \ln(c^{hf}_{t+i}) \bigg)\\ &\text{s.t}\\
&c^{hh}_t+c^{hf}_t(1+\tau_c)+ p^{h}_t s^{hh}_t+\frac{\Phi^h_s}{2}(s^{hh}_t)^2 =s^{hh}_{t-1}(p^{h}_t+d^{h}_t)\\
\end{align*}
Solve:
\begin{align}
&c^{hh}_t=c^{hf}_t(1+\tau_c)\\
&p^{h}_t=\beta E_t \bigg[\frac{c^{hh}_t}{c^{hh}_{t+1}} \bigg(  p^{h}_{t+1}+d^{h}_{t+1} \bigg) \bigg] - \Phi^h_s s^{hh}_t
\end{align}




















\subsection{Foreign household}
\emph{foreign} household owns domestic shares, \emph{foreign} shares and \emph{foreign} bonds. They spend dividends or sell assets to consume. In aggregate, consumption of \emph{foreign} goods cannot exceed \emph{foreign} share dividends. There are no holding cost on \emph{foreign} assets. 

\begin{align*}
&\max \Sigma_{i=0}^\infty \beta^i E_t \bigg(\ln(c^{ff}_{t+i})+ \ln(c^{fh}_{t+i}) \bigg)\\ &\text{s.t}\\
&c^{ff}_t+c^{fh}_t(1+\tau_c)+ p^{h}_t s^{fh}_t+\frac{\Phi^f_s}{2}(s^{fh}_t)^2 + p^{f}_t s^{ff}_t+ R_t b_t=g_t+s^{fh}_{t-1}(p^{h}_t+d^{h}_t)+s^{ff}_{t-1}(p^{f}_t+d^{f}_t)+b_{t-1}\\
\end{align*}
Solve:
\begin{align}
&c^{ff}_t=c^{fh}_t(1+\tau_c)\\
&p^{h}_t=\beta E_t \bigg[\frac{c^{ff}_t}{c^{ff}_{t+1}} \bigg(  p^{h}_{t+1}+d^{h}_{t+1} \bigg) \bigg] - \Phi^{f}_s s^{fh}_t\\
&p^{f}_t=\beta E_t \bigg[\frac{c^{ff}_t}{c^{ff}_{t+1}} \bigg(  p^{f}_{t+1}+d^{f}_{t+1} \bigg) \bigg]\\
&R_t=\beta E_t \bigg[\frac{c^{ff}_t}{c^{ff}_{t+1}} \bigg] 
\end{align}













\subsection{Foreign Government}
\emph{foreign} government issues risk free one period bond.
\begin{align}
&b_{t} = b_{ss}(1-\alpha^b) + \alpha^b b_{t-1} + \epsilon^b_t\\
&g_t	   = R_t b_{t}-b_{t-1}
\end{align}


\subsection{Firms}
\begin{align}
&s^{fh}_t+s^{hh}_t=1\\
&d^h_t=d^h_{ss} (1-\alpha^{sh}) +\alpha^{sh}_d d^h_{t-1} + \epsilon^{sh}_{t}\\
&d^f_t=d^f_{ss} (1-\alpha^{sf}) +\alpha^{sf}_d d^f_{t-1} + \epsilon^{sf}_{t}\\
\end{align}

\subsection{Aggregate budget constraints}
\begin{align}
&c^{hh}_t+c^{fh}_t=d^h_t - \tau_c c^{fh}_t -\frac{\Phi^{h}_s}{2}(s^{hh})^2 - \frac{\Phi^f_s}{2}(s^{fh})^2\\
&c^{hf}_t + c^{ff}_t = d^f_t - \tau_c c^{hf}_t
\end{align}





















\section{No adjustment cost in steady state. Infinite solutions}\label{AdjustmentCost}
\subsection{\emph{home} household with 2 period bond, 1 period bond and shares}
\begin{align*}
&\max \Sigma_{i=0}^\infty \beta^i u(c_{t+i})\\ &\text{s.t}\\
&c^{hh}_t+c^{hf}_t(1+\tau_c)+R^h_{2,t} b^{hh}_{2,t} + \frac{\Phi_b}{2}(b^{hh}_{2,t}-b^{hh}_{2,t-1})^2 +
R^h_{1,t} b^{hh}_{1,t} + \frac{\Phi_b}{2}(b^{hh}_{1,t}-b^{hh}_{1,t-1})^2 + p^{h}_t s^{hh}_t+\frac{\Phi_s}{2}(s^{hh}_t-s^{hh}_{t-1})^2\\
&=g^h_t+s^{hh}_{t-1}(p^{h}_t+d^{h}_t)+R^{h}_{1,t}b^{hh}_{2,t-1}+b^h_{1,t-1}\\
&R^h_{2,t} \equiv E_t\bigg(\frac{1}{(1+r_{t+1})(1+r_{t+2})} \bigg), R_{1,t} \equiv E_t\bigg(\frac{1}{1+r_{t+1}} \bigg)
\end{align*}
FOCs:
\begin{align*}
&\frac{1}{c^{hh}_t}=-\lambda_t\\
&\frac{1}{c^{hf}_t(1+\tau_c)}=-\lambda_t \\
&\lambda_t\big[R^h_{1,t}+\Phi_b (b^{hh}_{1,t}-b^{hh}_{1,t-1})\big ]+ \lambda_{t+1} \beta \big[\Phi_b (b^{hh}_{1,t} - b^{hh}_{1,t+1})]-\lambda_{t+1}\beta =0\\
&\lambda_t\big[R^h_{2,t}+\Phi_b (b^{hh}_{2,t}-b^{hh}_{2,t-1})\big ]+ \lambda_{t+1} \beta \big[\Phi_b (b^{hh}_{2,t} - b^{hh}_{2,t+1})]-\lambda_{t+1}\beta R^{h}_{1,t+1}=0\\
&\lambda_t \big[p^{h}_t + \Phi_s (s^{hh}_t-s^{hh}_{t-1})\big] + \lambda_{t+1} \beta \big[\Phi_s  (s^{hh}_t-s^{hh}_{t+1}) - p^{h}_{t+1}-d^{h}_{t+1}\big]=0
\end{align*}
Solve:
\begin{align}
&c^{hh}_t=c^{hf}_t(1+\tau_c)\\
&R^h_{1,_t}=\frac{c^{hh}_t}{c^{hh}_{t+1}}\beta \big[1+\Phi_b (b^{hh}_{1,t+1} - b^{hh}_{1,t})\big] -\Phi_b (b^{hh}_{1,t}-b^{hh}_{1,t-1})\\
&R^h_{2,_t}=\frac{c^{hh}_t}{c^{hh}_{t+1}}\beta \big[R^{h}_{1,t+1}+\Phi_b (b^{hh}_{2,t+1} - b^{hh}_{2,t})\big] -\Phi_b (b^{hh}_{2,t}-b^{hh}_{2,t-1})\\
&p^{h}_t=\frac{c^{hh}_t}{c^{hh}_{t+1}}\beta \bigg[ \Phi_s (s^{hh}_{t+1}-s^{hh}_t)+p^{h}_{t+1}+d^{h}_{t+1} \bigg] - \Phi_s (s^{hh}_t - s^{hh}_{t-1})
\end{align}

\subsection{\emph{foreign} household with global 1 period bond and all \emph{home} assets}
\begin{align*}
&\max \Sigma_{i=0}^\infty \beta^i u(c_{t+i})\\ &\text{s.t}\\
&c^{ff}_t+c^{fh}_t(1+\tau_c)+R^h_{2,t} b^{fh}_{2,t} + \frac{\Phi_{bfh}}{2}(b^{fh}_{2,t}-b^{fh}_{2,t-1})^2 +
R^h_{1,t} b^{fh}_{1,t} + \\ 
&\frac{\Phi_{bfh}}{2}(b^{fh}_{1,t}-b^{fh}_{1,t-1})^2 + p^{h}_t s^{fh}_t+\frac{\Phi_{sfh}}{2}(s^{fh}_t-s^{fh}_{t-1})^2+R^f_{1,t}b^f_{1,t}+p^h_t s^{ff}_t\\&=g^f_t+s^f_{t-1}*(p^f_t+d^f_t+)s^{fh}_{t-1}(p^{h}_t+d^{h}_t)+R^{h}_{1,t}b^{fh}_{2,t-1}+b^h_{1,t-1}+b^f_{1,t-1}\\
\end{align*}


FOCs:
\begin{align*}
&\frac{1}{c^{ff}_t}=-\lambda^f_t\\
&\frac{1}{c^{fh}_t(1+\tau_c)}=-\lambda^f_t \\
&\lambda^f_t [R^f_{1,t}]-\lambda^f_{t+1}*\beta=0\\
&\lambda^f_t\big[R^h_{1,t}+\Phi_{bfh} (b^{fh}_{1,t}-b^{fh}_{1,t-1})\big ]+ \lambda^f_{t+1} \beta \big[\Phi_{bfh} (b^{fh}_{1,t} - b^{fh}_{1,t+1})]-\lambda^f_{t+1}\beta =0\\
&\lambda^f_t\big[R^f_{2,t}+\Phi_{bfh} (b^{fh}_{2,t}-b^{fh}_{2,t-1})\big ]+ \lambda^f_{t+1} \beta \big[\Phi_{bfh} (b^{fh}_{2,t} - b^{fh}_{2,t+1})]-\lambda^f_{t+1}\beta R^{h}_{1,t+1}=0\\
&\lambda^f_t \big[p^{h}_t + \Phi_{sfh} (s^{fh}_t-s^{fh}_{t-1})\big] + \lambda^f_{t+1} \beta \big[\Phi_{sfh}  (s^{fh}_t-s^{fh}_{t+1}) - p^{h}_{t+1}-d^{h}_{t+1}\big]=0
\end{align*}
Solve:
\begin{align}
&c^{ff}=c^{fh}(1+\tau_c)\\
&R^f_{1,t}=\frac{c^{ff}_t}{c^{ff}_{t+1}}\beta\\
&R^h_{1,t}=R^f_{1,t} \big[1+\Phi_{bfh} (b^{fh}_{1,t+1} - b^{fh}_{1,t})\big] -\Phi_{bfh} (b^{fh}_{1,t}-b^{fh}_{1,t-1})\\
&R^h_{2,_t}=R^f_{1,t} \big[R^{h}_{1,t+1}+\Phi_{bfh} (b^{fh}_{2,t+1} - b^{fh}_{2,t})\big] -\Phi_{bfh} (b^{fh}_{2,t}-b^{fh}_{2,t-1})\\
&p^{h}_t=R^f_{1,t} \big[ \Phi_{sfh} (s^{fh}_{t+1}-s^{fh}_t)+p^{h}_{t+1}+d^{h}_{t+1} \big] - \Phi_{sfh} (s^{fh}_t - s^{fh}_{t-1})\\
&p^f_t=R^f_{1,t}\big[p^f_{t+1}+d^f_{t+1}\big]
\end{align}

\subsection{Governments}
\emph{home} government:
\begin{align}
&b^h_{1,t} = b^{hh}_{1,t} + b^{fh}_{1,t}\\
&b^h_{2,t} = b^{hh}_{2,t} + b^{fh}_{2,t}\\
&b^h_{1,t} = b^h_{2,t-1}\\
&b^h_{2,t} = (1-\alpha^h_{b})+\alpha^h_{b} b^h_{2,t-1}+\epsilon^h_{b,t}\\
&g^h_t	   = b^h_{2,t}R^h_{2,t}-b^h_{2,t-2}
\end{align}
\emph{foreign} government:
\begin{align}
&b^f_{1,t} = (1-\alpha^f_b) + \alpha^f_b b^f_{1,t-1}+\epsilon^f_{b,t}\\
&g^f_t 	= b^f_{1,t} R^f_{1,t}-b^f_{1,t-1}
\end{align}


\subsection{Firms}
\begin{align}
&s^{fh}_t+s^{hh}_t=1\\
&d^h_t=d^h_{ss} (1-\alpha^h_d) +\alpha^h_d d^h_{t-1} + \epsilon^h_{d,t}\\
&d^f_t=d^f_{ss} (1-\alpha^f_d) +\alpha^f_d d^f_{t-1} + \epsilon^f_{d,t}
\end{align}

\subsection{Aggregate budget constraints}
\begin{align}
&c^{hh}_t+c^{fh}_t=d^h_t - \tau_c c^{fh}_t -\frac{\Phi_b}{2}(b^{hh}_{2,t}-b^{hh}_{2,t-1})^2 - \frac{\Phi_b}{2}(b^{hh}_{1,t}-b^{hh}_{1,t-1})^2\\ \nonumber &-\frac{\Phi_s}{2}(s^{hh}_t-s^{hh}_{t-1})^2 - \frac{\Phi_{bfh}}{2}(b^{fh}_{2,t}-b^{fh}_{2,t-1})^2 -\frac{\Phi_{sfh}}{2}(s^{fh}_t-s^{fh}_{t-1})^2\\
&c^{hf}_t + c^{ff}_t = d^f_t - \tau_c c^{hf}_t
\end{align}
\end{document}